\cvsection{Experience}
\begin{cventries}
  \techentries
    {LEAD Frontend Developer}
    {CODIX}
    {Tunis, Tunisia}
    {October. 2017 - Now}
    {
      \begin{cvitems}
        \item {Frontend development of Web Interfaces of IMX a financial solution developed by CODIX }
        \item {Leading and assistance of Tunisia frontend TEAM. Helping them fix code issues , advocating coding best practices, doing code review and monitoring their tasks progress }
      \end{cvitems}
	\vspace{10pt}\textbf{ Achievements:}
      \begin{cvitems}
	{\vspace{14pt}}
        \item {Developing and intervening on hundreds of interfaces linked to the IMX solution while taking in account its critical specifications and contributing to the major technological switch of the solution from a heterogeneous architecture desktop application to a modern web application. }
        \item {Build a Tunisian Frontend Team as one of the 2 other Frontend teams among CODIX in Bulgaria and Vietnam, dealt with the process of the hire. }
      \end{cvitems}
    }
    {\textcolor{awesome}{Technologies/Tools: } {\color{graytext}}  {Angular, AngularJs, Typescript, NPM, HTML5, GIT, SQL, FORMS}}
	{} 
    { 
    }
  \techentries
    {Frontend Developer/Backend Developer}
    {OCTOPOUCE}
    {Quatre Bornes, Mauritius}
    {DEC. 2016 - Jun. 2017}
    {
      \begin{cvitems}
        \item {Working among a team composed of different nationalities, my task involve handling the frontend development of the website for European and local Mauritian clients, Mockup integration and handling issues of multiple browsers and little devices responsive web design (IE9, SAFARI, Iphone4). On some projects, accessibility issues were handled. I have also to intervene on backend native PHP and wordpress projects.}
      \end{cvitems}
	\vspace{10pt}\textbf{ Achievements:}
      \begin{cvitems}
	{\vspace{14pt}}
        \item {Worked as Frontend Developer, delivering for different projects with different technologies (mainly angularJs), client were mainly European (Publicis Groupe, Hello Agency) and local like Anahita hotel }
      \end{cvitems}
    }
    {\textcolor{awesome}{Technologies/Tools: } {\color{graytext}}  {AngularJs, jQuery, CSS3/SASS, Bootstrap, GULP, Webpack, HTML5, GIT, wordpress.}}
    {Urls:} 
    { \href{http://anahita.mu/}{\color{graytext}{\hspace{1cm}\underline{http://anahita.mu/}} \break
    }}
  \techentries
    {Frontend Developer/Backend Developer}
    {PI2R}
    {Tunis, Tunisia}
    {Feb. 2016 - Nov. 2016}
    {
      \begin{cvitems}
        \item {I have to realize BackEnd and FrontEnd interventions on several websites for multiple Tunisian clients and I was part of a French / Tunisian team that worked on a delivery project concerning the development of a customer web content management system. }
      \end{cvitems}
    }
    {\textcolor{awesome}{Technologies/Tools: } {\color{graytext}}  {PHP5, symphony, mysql, wordpress, jQuery, CSS3, Bootstrap}}
    {Urls:} 
    {
    \href{http://www.milddream.com/fr/ }{\color{graytext}{\hspace{1cm}\underline{http://www.milddream.com/fr/ }}} \break
    \href{http://www.ozeol.com/fr/}{\color{graytext}{\hspace{1cm}\underline{http://www.ozeol.com/fr/}}} \break
    } 
  \techentries
    {Backend Developer/Frontend Developer}
    {Skopeo}
    {Tunis, Tunisia}
    {Jul. 2014 - May. 2015}
    {
      \begin{cvitems}
        \item {Geo-location web solutions and E-Commerce solutions web development having to in backend (native PHP and CMS) and frontend scopes.}
      \end{cvitems}
\vspace{10pt}\textbf{ Achievements:}
      \begin{cvitems}
	{\vspace{14pt}}
        \item {Contributing as backend/frontend developer in the Developing of Geo-location and cars reservation solution for the Gabon ministry of transport that started the initial phase of test Taxi tasso}
        \item {Implementing payment module used in Togo for soukexpert an e commerce web site  }
        \item {Total backend/frontend rebuild or code refactoring of existing web site used for annouces (CarAFRICA, Darafrica)   }
        \item {participating in experimental geolocation solutions as backend developer (stock Manager, Geotrack)   }
      \end{cvitems}
    }
    {\textcolor{awesome}{Technologies/Tools: } {\color{graytext}}  {php5, prestashop, HTML5, jQuery , google map, Mysql}}
     {Urls:} 
    {
    \href{http://www.skopeo.fr/solutions.html }{\color{graytext}{\hspace{1cm}\underline{http://www.skopeo.fr/solutions.html }}} \break
    }          
  \techentries
    {Backend Developer/Frontend Developer}
    {Direct Engineering}
    {Tunis, Tunisia}
    {Sep. 2013 - May. 2014}
    {
      \begin{cvitems}
        \item {Web development of web interfaces and web scrapping and announces injection. }
      \end{cvitems}
	\vspace{10pt}\textbf{ Achievements:}
      \begin{cvitems}
	{\vspace{14pt}}
        \item {Developed several scripts scrapping announces from API and injected on the database of several clients in production mode (pure jobs, jeveux1truc) }
      \end{cvitems}
    }
    {\textcolor{awesome}{Technologies/Tools: } {\color{graytext}}  {PHP,magic-parser,Joomla!,KWO , jQuery,MySQL.}}
    {Urls:} 
    {\href{http://www.pure-jobs.com/}{\color{graytext}{\hspace{1cm}\underline{http://www.pure-jobs.com/}}} \break
    }       
\end{cventries}
